% Maxim Kraynov Resume
% URL: 
%
% Based on resume tex file by Kamil Wojcicki
% URL: http://linux.dsplabs.com.au/resume-writing-example-latex-template-linux-curriculum-vitae-professional-cv-layout-format-text-p54/

\documentclass[margin,line]{resume}

\usepackage{graphicx}

\begin{document}
\vspace{50mm}
\name{\huge Maxim Kraynov}
{
	\sc
    \hfill +4915222808576                  \vspace{0mm}\\\vspace{0mm}%
    \hfill me@maxkraynov.net            \vspace{0mm}\\\vspace{-10mm}%
\vspace{1mm}
}


\begin{resume}

\vspace{1mm}

    %__________________________________________________________________________________________________________________
    % Interests
    \section{\mysidestyle \textbf{\large{A}\small{BOUT\\}}}

	I’m Java Software Developer with 7+ years of hands-on experience, specialized in high-load server-side and web-based applications development on Java. DevOps fan. People say I have good communication skills.


\sectionline

    %__________________________________________________________________________________________________________________
    % Computer Skills
    \section{\mysidestyle \textbf{\large{S}\small{KILLS}}}

    Java,\hspace{2mm}Spring,\hspace{2mm}SQL,\hspace{2mm}Golang,\hspace{2mm}Ansible,\hspace{2mm}Jenkins,\hspace{2mm}Docker,\hspace{2mm}Bash.


\sectionline

    %__________________________________________________________________________________________________________________
    % Professional Experience
    \section{\mysidestyle \textbf{\large{P}\small{ROFESSIONAL\\EXPERIENCE}}}

    % Zooplus
    \textbf{\listing Zooplus}, Munich \vspace{2mm}\\\vspace{1mm}%
    \textsl{Senior Software Engineer} \hfill \textbf{Mar 2018 – July 2019}\\
    Developed e-commerce payment platform for online shop. \vspace{1mm}

    % Getintent
    \textbf{\listing Getintent}, Moscow \vspace{2mm}\\\vspace{1mm}%
    \textsl{Senior Software Engineer (Data Team)} \hfill \textbf{Feb 2017 – July 2017}\\
    Wrote MapReduce jobs with the Data Science team to analyze data. \vspace{1mm}

    \textsl{Senior Solution Consultant} \vspace{2mm}\hfill \textbf{Oct 2015 – Feb 2017}\\
    Designed and developed Getintent RTBSuite -- software solution which allows companies to build their own DSPs. Worked on site (Los Angeles, US), developed and deployed custom DSP, consulted client's sysops and developers. \vspace{1mm}

    \textsl{Senior Software Engineer} \vspace{2mm}\hfill \textbf{Apr 2014 – Oct 2015}\\
    Participated in high-load, low-latency DSP solution development (5000 QPS per server).

    % Alfa
    \textbf{\listing Alfa-bank / Alfa-Laboratory}, Moscow \vspace{2mm}\\\vspace{1mm}%
    \textsl{Software Engineer} \hfill \textbf{Oct 2011 – Mar 2014}\\
    Participated in development of high-load, low-latency, 24/7 internet-banking system from the beginning to the successful release.

    % I.T. Co.
    \textbf{\listing I.T. Co.}, Moscow \vspace{2mm}\\\vspace{1mm}%
    \textsl{Software Engineer} \hfill \textbf{Oct 2010 – Oct 2011}\\
    Participated in project ``Development and deployment ECM system for Tele2 Russia''
    

\sectionline

    %__________________________________________________________________________________________________________________
    % Education
    \section{\mysidestyle \textbf{\large{E}\small{DUCATION}}}

    \textbf{\listing National Research University of Electronic Technology}, Moscow \vspace{2mm}\\\vspace{1mm}%
    \textsl{Computer Science, Master's degree} \hfill \textbf{2010 -- 2012}\vspace{-3mm}\\\vspace{-1mm}%
    \vspace{-1.5mm}

    \textbf{\listing National Research University of Electronic Technology}, Moscow \vspace{2mm}\\\vspace{1mm}%
    \textsl{Electronics and Microelectronics, Bachelor's degree} \hfill \textbf{2006 -- 2010}\vspace{-3mm}\\\vspace{-1mm}%
    \vspace{-1.5mm}

\sectionline

    %__________________________________________________________________________________________________________________
    % Certificates
    \section{\mysidestyle \textbf{\large{C}\small{ERTIFICATES}}}

    \textbf{\listing Web services development with Golang} \vspace{2mm}\\\vspace{1mm}%
    \textsl{Coursera, Moscow Institute of Physics and Technology} \hfill \textbf{Jan 2019}\vspace{-3mm}\\\vspace{-1mm}%
    \vspace{-1.5mm}

    \textbf{\listing Algorithms} \vspace{2mm}\\\vspace{1mm}%
    \textsl{Coursera, Stanford University} \hfill \textbf{Jun 2017}\vspace{-3mm}\\\vspace{-1mm}%
    \vspace{-1.5mm}

\sectionline


\end{resume}
\end{document}